Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-04 paperICSME.tex
Añadiendo algunos comentarios para mejorar

There are several research articles that suggest improvements to the SZZ algorithm. Kim et al.~\cite{kim2006automatic} use annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion. Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments. Williams et al. have revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}.

@@

%\grex{Quizas mirar si hay mas articulos en esta linea. No es muy importante esto.}

@@

\subsection{Fist Stage: Filtering}
\label{sec:firstStage}

@@

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

@@

\begin{itemize}
    \item Exclusively blank lines
    \item Changes in the format
    \item Copied lines
    \item Changes in source code comments
    \item Updates in the version number of a file/software 
\end{itemize}

@@

%\begin{enumerate}
% \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se ha anadido codigo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo. 
% \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han anadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la linea se olvido de realizar dichas comporbaciones, y en ese caso seria el causante del bug. Pero existen casos que la comprobacion que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error. Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provoco el error, porque realmente era dificil saberlo.
% \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
%\end{enumerate}

>>>>

There are several research articles that suggest improvements to the SZZ algorithm. Kim et al.~\cite{kim2006automatic} use annotation graphs instead of CVS annotation to locate, in the previous versions, the lines affected by modification and deletion. Also, they avoid some false positives by not considering blank spaces, changes in the format or changes in the comments. Williams et al. have revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}. 
\gema{mirar como se nombra en[20] porque uno de los revisores nos dijo : "Shouldn't 1(2) be named 'Bug-inducing' instead of 'Fix-inducing'?"}

@@

\gema{Anadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

@@

\subsection{First Stage: Filtering}
\label{sec:firstStage}

@@

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. \gema{Esto es lo que dijo uno de los revisores sobre este parrafo : "First, the rule is unclear for me. Do you mean an update to the ticket? The code? The review? Second, the rationale is unclear and unsupported. Why would such an update indicate that a bug was present?" Deberíamos modificarlo}
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

@@

\begin{itemize}
    \item Exclusively blank lines
    \item Changes in the format
    \item Copied lines
    \item Changes in source code comments
    \item Updates in the version number of a file/software 
    \item These commits that were committed after the bug report was opened in Launchpad, according to to \'Sliwerski et al. ~\cite{sliwerski2005changes}.
\end{itemize}

@@

\gema{Esto es otra de las cosas que los revisores comentaron y debemos discutir: "Kim et al. [14] and Williams et al. [20] also manually analyze samples of SZZ data. However, they report much higher percentages of correct SZZ results. Potential reasons for the discrepancies should be discussed."}

\gema{Otra cosa que tenemos que mencionar en el paper de acuerdo con los revisores: "it is unclear how the community can move forward from here? Since abandoning SZZ altogether is unreasonable (without proposing an alternative), can you offer advice based on findings that would help to improve SZZ? For example, an analysis of the bug fixes that mistakenly blame the previous version of those lines would likely shed some light onto how SZZ could be improved"}
%\begin{enumerate}
% \item No todos los casos son tan claros como los mostrados en los ejemplos, hay ocasiones en las que solo se ha anadido codigo y no somos capaces de encontrar al responsable por que no existe ninguna manera de poder identificar al commit previo. 
% \item Hemos sido conservadores, en ocasiones cuando se han modificado lineas como if/else y se han anadido comprobacione que anteriormente no estaban, se puede pensar que el commit previo que toco la linea se olvido de realizar dichas comporbaciones, y en ese caso seria el causante del bug. Pero existen casos que la comprobacion que se necesita en el if ha aparecido porque se introdujo una nueva funcionalidad, por stanto en el momento original en el que se escribio la linea por primera vez no habia ningun error. Por tanto a menos que se descrisba esta ultima situacion en la descripcion del commit o del bug report, he considerado la idea treadicional, que el commit anterior provoco el error, porque realmente era dificil saberlo.
% \item Hemos utilizado la herramienta porque es un proceso complicado. Para la primera parte de decidir si es o no es un bug report hemos tenido que desarrollar la herramienta.
%\end{enumerate}
